\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-03 paper.tex
made requested changes

Even once the idea for ARuko was settled on audio tour functionality with 
additional AR components, what exactly those AR components would do was still
undecided for a while. Atticus knew he wanted to use AR on the tour, but wasn't
sure what to do with it. At first, we made recommendations to him based on the
capabilities of Vuforia that we found in our research. We knew it was good at
image recognition and ground plane recognition, so we suggested that maybe 
displaying some sorts of 3D models in certain locations using either of these
features might be an interesting way to expand on the tour. With these 
recommendations in mind, Atticus expressed interest in the capability of using
building facades as image targets. The intention then would be to tie content
related to a specific location within Kinkaku-ji to that physical location, and
use images of the location as targets. As previously explained, this ultimately
did not work out due to the limitations of image recognition with Vuforia.

After being initially deterred from image recognition, we thought that ground
and mid-air plane recognition might the best way to implement AR in the app. 
It didn't have to rely on images that meet Vuforia's criteria, and since it 
could be triggered anywhere, it seemed like a good fit for an app focusing on
walking around a site. Atticus explained that he primarily wanted to use AR to
display art related to the site. So we focused our efforts with ground and 
mid-air plane AR on ways to display 2D images. What we ended up creating first
was a feature that allowed you to view certain images in AR, using ground plane
detection, based on what region you were in. So when you entered a region of 
the tour, the image menu would be dynamically populated with buttons that, when
tapped, would create a Plane primitive in Unity with the given image displayed
on it and place it on the ground plane.

We encountered a few notable problems with this though. One problem was that 
the Plane we made was always the same size and dimensions, and would cause 
images to stretch to fit the plane. Further testing to change the size of the
plane with each picture proved difficult. Additionally, using a Plane primitive
had problematic effects on the way the object was lit in the Unity scene, as 
well as how it appeared when not viewed head-on. If viewed from an angle, the 
picture could become very dark and difficult to see. And if viewed from behind,
it would actually be completely invisible. Because of these issues, we decided
to place the images on a 3D Cube primitive instead. But after showing this
feature to Atticus during early testing at Kinkaku-ji, he decided that he 
wanted to move away from displaying images in AR. Looking back, the feature
may have worked better with mid-air plane recognition so that the user could
place the image directly in front of them.

@@

On Monday, September 9th, Atticus approached us about an additional project he 
wanted us to tackle. He wanted us to adapt Kyoto VR's NOxAR app to use ground
plane detection. Currently, the NOxAR app is an AR app for Microsoft Hololens
that uses image targets with Vuforia. When viewing the correct image target,
the app projects a 3D model of a Noh Theater\footnote{A form of Japanese 
theater originating in the 14th century structured around song and slow 
dancing~\autocite{japanguide2018}.} performer dancing to background 
music~\autocite{noxar2018}. What Atticus wanted us to do was have the app use 
ground plane detection in order to display the Noh performer so that it could 
be displayed anywhere. Additionally, he wanted us to scale up the model so that
when displayed in AR, the performer would appear life-sized, as if she were 
really there dancing in the real world.

For this project, Atticus sent us the original Unity project files for NOxAR.
We then had to figure out how to turn the original project into a ground plane
AR app. At first we tried importing the assets for the Noh performer into a new
Unity project. We did this for a couple reasons. The first reason was because
we didn't want all of the extra components of the original NOxAR project to
get in the way of what we were trying to do. We also did this because the %could probably put an example pic here
original project was made with a 2017 version of Unity, so we wanted to try to
use our more recent version so we wouldn't risk running into any depricated 
features or functionalities. We did eventually get this method to work, but the
model of the Noh performer was lacking a lot of the details that the original 
model had. This was attributed to poor importation of the original assets, so 
we decided to try making changes to the original NOxAR project instead.

Per Atticus's advice, we deleted any and all unnecessary elements from the 
scene before proceeding. We also updated the Unity version of the project to
the 2019 version we were using, and updated the version of Vuforia to the most
recent version, neither of which created any problems. The process of getting
the model to appear on ground plane detection instead of image target 
recognition was relatively simple. We simply moved the model from an image 
target to a simulated ground plane, added a plane detector component to the
scene, and made sure the Vuforia settings were in place for ground plane
detection to work well. From there, we just had to test the app a few times so
we could properly scale the model to life size. So on Tuesday, September 17th, 
we completed the NOxAR ground plane adaptation to Atticus's saisfaction and
sent him the final APK file for the app.

>>>>

Even once the idea for ARuko was settled on audio tour functionality with 
additional AR components, what exactly those AR components would do was still
undecided until more details about the project crystallized. Atticus knew he 
wanted to use AR on the tour, but was not sure what to do with it. At first, we
made recommendations to him based on the capabilities of Vuforia that we found 
in our research. We knew it was good at image recognition and ground plane 
recognition, so we suggested that maybe displaying some sorts of 3D models in 
certain locations using either of these features might be an interesting way to
expand on the tour. With these recommendations in mind, Atticus expressed 
interest in the capability of using building facades as image targets. The 
intention then would be to tie content related to a specific location within 
Kinkaku-ji to that physical location, and use images of the location as 
targets. As previously explained, this ultimately did not work out due to the 
limitations of image recognition with Vuforia.

After being initially deterred from image recognition, we thought that ground
and mid-air plane recognition might the best way to implement AR in the app. 
It did not have to rely on images that meet Vuforia's criteria, and since it 
could be triggered anywhere, it seemed like a good fit for an app focusing on
walking around a site. Atticus explained that he primarily wanted to use AR to
display art related to the site. With this in mind, we focused our efforts with
ground and mid-air plane AR on ways to display 2D images. What we ended up 
creating first was a feature that allowed users to view certain images in AR, 
using ground plane detection, based on what region you were in. When users 
entered a region of the tour, the image menu would be dynamically populated 
with buttons that, when tapped, would create a Plane primitive in Unity with 
the given image displayed on it and place it on the ground plane.

We encountered a few notable problems with this though. One problem was that 
the Plane we made was always the same size and dimensions, and would cause 
images to stretch to fit the plane. Further testing to change the size of the
plane with each picture proved difficult. Additionally, using a Plane primitive
had problematic effects on the way the object was lit in the Unity scene, as 
well as how it appeared when not viewed head-on. If viewed from an angle, the 
picture could become very dark and difficult to see. If viewed from behind,
back-face culling would take effect and the plane would become completely 
invisible. Because of these issues, we decided to place the images on a 3D Cube
primitive instead. But after showing this feature to Atticus during early 
testing at Kinkaku-ji, he decided that he wanted to move away from displaying 
images in AR. Looking back, the feature may have worked better with mid-air 
plane recognition so that the user could place the image directly in front of 
them.

@@

On Monday, September 9\textsuperscript{th}, Atticus approached us about an additional project he 
wanted us to tackle. He wanted us to adapt Kyoto VR's NOxAR app to use ground
plane detection. Currently, the NOxAR app is an AR app for Microsoft Hololens
that uses image targets with Vuforia. When viewing the correct image target,
the app projects a 3D model of a noh theater\footnote{A form of Japanese 
theater originating in the 14th century structured around song and slow 
dancing~\autocite{japanguide2018}.} performer dancing to background 
music~\autocite{noxar2018}. What Atticus wanted was to have the app use 
ground plane detection in order to display the noh performer so that it could 
be displayed anywhere. Additionally, he wanted us to scale up the model so that
when displayed in AR, the performer would appear life-sized.

For this project, Atticus sent us the original Unity project files for NOxAR.
We then had to figure out how to turn the original project into a ground plane
AR app. At first we tried importing the assets for the noh performer into a new
Unity project. We did this for a couple reasons. The first reason was because
we did not want all of the extra components of the original NOxAR project to
get in the way of what we were trying to do. We also did this because the %could probably put an example pic here
original project was made with a 2017 version of Unity, so we wanted to try to
use our more recent version so we would not risk running into any depricated 
features or functionalities. We did eventually get this method to work, but the
model of the noh performer was lacking a lot of the details that the original 
model had. This was attributed to poor importation of the original assets, so 
we decided to try making changes to the original NOxAR project instead.

Per Atticus's advice, we deleted any and all unnecessary elements from the 
scene before proceeding. We also updated the Unity version of the project to
the 2019 version we were using, and updated the version of Vuforia to the most
recent version, neither of which created any problems. The process of getting
the model to appear on ground plane detection instead of image target 
recognition was relatively simple. We simply moved the model from an image 
target to a simulated ground plane, added a plane detector component to the
scene, and made sure the Vuforia settings were in place for ground plane
detection to work well. From there, we just had to test the app a few times so
we could properly scale the model to life size. On Tuesday, September 17th, 
we completed the NOxAR ground plane adaptation to Atticus's saisfaction and
sent him the final APK file for the app.
